---
title: "P8105_HW6_AA4266"
author: "Abhishek Ajay (aa4266)"
date: "November 25, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      fig.width = 6,
                      fig.asp = .6,
                      out.width = "90%"
                      )

library(tidyverse)
library(rvest)
library(purrr)
library(ggplot2)
library(broom)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

#Problem 1

Here we work on the homicides data from 50 large U.S. cities that has been gathered by The Washington Post.

**Data Import**
```{r p1_import}
hom_data = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(city_state = paste(city, state, sep = ", "), 
         disposition = as.factor(disposition),
         bin_disposition = as.numeric(disposition == "Closed by arrest")) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")),
         victim_race != "Unknown") %>% 
  mutate(victim_race = ifelse(victim_race == "White", "white", "non-white"),
         victim_race = fct_relevel(victim_race, "white"),
         victim_age = as.numeric(victim_age))
```
In bin_disposition, **1** means, Closed by arrest and **0** means elsewise. I removed the victims with Unknown races to avoid bias in the estimation.

Now we fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. 

```{r p1_baltimore_glm}
hom_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(bin_disposition ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
  broom::tidy(exponentiate = TRUE, conf.int = TRUE) %>% 
  filter(term == "victim_racenon-white") %>% 
  select(OR = estimate, conf.low, conf.high) %>% 
  knitr::kable(digits = 3)
```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r p1_all_cities_glm}
fit_logistic_all_OR = 
  hom_data %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(bin_disposition ~ victim_age + victim_sex + victim_race, data = ., family = binomial())), 
         results = map(.x = models, ~ broom::tidy(.x, exponentiate = TRUE, conf.int = TRUE))) %>% 
  select(-data, -models) %>% 
  unnest() %>% 
  filter(term == "victim_racenon-white") %>% 
  select(city_state, OR = estimate, conf.low, conf.high)
  
fit_logistic_all_OR %>% 
  head() %>% 
  knitr::kable(digits = 3)
```

The above table shows the top 6 cities with the highest odds ratio of solving homicides comparing non-white victims to white victims. 


Following will be a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r p1_all_cities_glm_plot}
fit_logistic_all_OR %>% 
  mutate(city_state = as.factor(city_state), 
         city_state = fct_reorder(city_state, desc(OR))) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(color = "#993333", angle = 90, size = rel(0.8), hjust = 1))
```